---
title: "Evidence, Policy and the Places in Between"
subtitle: "Guest Lecture for *Administered Societies*"
author: "Petr Bouchal"
date: 12 May 2022, FSV UK
output:
  xaringan::moon_reader:
    css: [xaringan-themer.css, slides.css]
    lib_dir: libs
    yolo: false
    mathjax: NULL
    includes:
      in_header: meta.html
    seal: true 
    nature:
      ratio: 16:9
      slideNumberFormat: ""
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      titleSlideClass: [bottom, left, inverse]
      beforeInit: "macros.js"

---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(fig.retina = 3, echo = F,
                      cache = F,
                      warning = F,
                      comment = "",
                      dev = "ragg_png",
                      fig.showtext = T,
                      message = F)
library(fontawesome)
library(tidyverse)
library(ptrr)
library(ragg)
library(knitr)

library(xaringanExtra)
library(flipbookr)

ptrr::set_geom_defaults()
ptrr::set_ptrr_ggplot_fonts()
update_geom_defaults("rect", list(fill = "blue"))

options(tibble.print_min = 20)
```

```{r, include=FALSE}
xaringanExtra::use_xaringan_extra("share_again")

xaringanExtra::style_share_again(
  share_buttons = c("twitter", "linkedin", "pocket")
)

xaringanExtra::use_extra_styles(
  hover_code_line = TRUE,         
  mute_unhighlighted_code = TRUE  
)
```


```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_mono_accent(
  base_color = "#0000ff",
  header_font_google = google_font("IBM Plex Sans"),
  text_font_google   = google_font("IBM Plex Sans"),
  code_font_google   = google_font("IBM Plex Mono"),
  table_row_even_background_color = "fff"
)
```

```{r fonts, include=FALSE}
ptrr::register_plexsans()
ptrr::register_plexsans_condensed()
```

```{r meta, include=FALSE}
library(metathis)
meta() %>%
  meta_general(
    description = "Description",
    generator = "xaringan and remark.js"
  ) %>% 
  meta_name("github-repo" = "petrbouchal/fsv2022") %>% 
  meta_social(
    title = "Title",
    url = "https://petrbouchal.xyz/xxx",
    image = "https://petrbouchal.xyz/xxx/slides/twitter_card.png",
    image_alt = "social alt",
    og_type = "website",
    og_locale = "cs_CZ",
    og_author = "Petr Bouchal",
    twitter_card_type = "summary_large_image",
    twitter_creator = "@petrbouchal"
  ) %>% 
  write_meta("meta.html")
```

class: left, middle, inverse

# Why you might want to listen to me

---

class: left, middle, medium

.pull-left[

Led strategy and evaluation units at Ministry of Reg. Dev't, Prague IPR, & a consulting firm

Do external analysis for government and NGO's, mostly using public data

]

.pull-right[

Also do research on government: Czech Priorities, IDEA CERGE-EI, ex-Institute for Government (UK)

Projekt PANK: supporting analytical capacities in gov

]

---
class: left, middle, large

 1\. Looking at evidence a good way to think through how gov't works

--

 2\. You can find yourselves in researcher / gov analyst roles

--

 3\. Knowledge of PA concepts helps explain puzzles about policy & evidence 

---



class: left, middle, inverse

# Some core questions

---
class: left, middle, large

 # 1\. What is policy?

---
class: large

# Some provocations

- not just what politicians decide
- one policy ≠ one place in government
- does not happen in a linear way
- blurry line between "policy" and "implementation"

---
class: left, middle, large

 # 2\. What is evidence?

---
class: large

# Some provocations

- not just research
- (what is good evidence?)
- what questions? ("What works?" Any others?)
- what researchers consider evidence x what gov considers
- useful term? What about "knowledge"? "Learning?"

---
class: left, middle, large

 # 3\. Why is evidence not used?

---
class: left, middle, large

# Some ideas

- a gap between two worlds?
- a supply x demand mismatch?
- an organisational issue? psychological factors?
- a skills issue?
- misunderstanding how policy works?
- how useful is learning from medicine, public health, education?
- cf. knowledge brokering, policy labs

---
class: large

# Trying to help: project hypotheses

--
- work at the team level
--

- address processes, ways of working, not just structures and skills
--

- some evidence on what works for getting evidence used, not much on improving "evidence work" generally in practice
--

- adapt existing good practices, learn from what happens

---
class: medium

# What does it look like in the wild?

- wide variety of evidence work and organisational setups: from data teams to policy & admin teams

--

- few overarching standards for "evidence work"
  - no official recognition of "analyst" as a role or profession
  - ditto for "evidence use" as a basic skill of a public official
  - emerging bottom-up professional community
  - many analytical roles only within ad-hoc projects
  
---
class: medium

# What does it look like in the wild? cont'd

- islands of excellence for specific types of evidence work
--

- lots of "small" policy at working/operational level
- much potential in using evidence to improve implementation and connect parts of the system, build feedback loops

---
class: large

# For the budding public officials: what kinds of skills are needed?

- doing basic policy analysis
- user focus, user/stakeholder engagement & rsrch
- whole system thinking
- evidence literacy, evidence synthesis
- data literacy and data analysis skills
- data and knowledge management
- management skills and habits

---
class: center, middle, inverse?

Thoughts?

---

class: center, middle, large


[petrbouchal.xyz/fsv2022](https://petrbouchal.xyz/fsv2021)

[pank.cz](https://pank.cz)

[ceskepriority.cz](https://ceskepriority.cz)

---

class: inverse, bottom, right, large
layout: false

<a href="https://twitter.com/petrbouchal">`r fa("twitter", fill = "white")`</a> <a href="https://github.com/petrbouchal">`r fa("github", fill = "white")`</a> <a href="https://linkedin.com/in/petrbouchal">`r fa("linkedin", fill = "white")`</a> petrbouchal  
[petrbouchal.xyz](https://petrbouchal.xyz)  
pbouchal@gmail.com





